Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2016-01-05 src/tf-cutcell-comparison/responses2.tex
justify sample line position

\begin{quotation}
	Section 4d – Sch\"{a}r mountain-wave tests. These tests are more interesting now that 
 the case has been simulated with a variety of grid resolutions. However, I'm 
 surprised that the analyses of these results seem to focus on behavior far 
 downstream of the mountain, as is evident in Figs. 6 and 7. I'm not aware of any 
 published results that extend beyond x = 25 km in Fig. 6. Since the amplitude of the 
 disturbances are decaying with downstream distance, small inaccuracies in behavior 
 of the absorbing layer and boundary conditions have larger impact such that the 
 relative errors in comparison to the analytic solution become large. (Note, for 
 example the erroneous extension of negative perturbation theta contours to the 
 surface at x = 25 km in Fig. 6.)  All we learn from Fig. 7b is that errors in theta near 
 the surface in the cut-cell cases, which must have been produced in the vicinity of the 
 terrain, continue to be swept downstream. I think it would be more informative to 
 focus on solution differences between the BTF and cut-cell results near the terrain as 
 is done in Fig. 8 for the terrain-following theta advection. The authors could display 
 these difference fields for the various grid resolutions in exactly the same manner as 
 in Fig. 8. The theta advection test presented by the authors is a very nice complement 
 to the gravity-wave tests. It confirms that the BTF solution is behaving properly and 
 therefore lends support to interpreting differences in the two grids as inaccuracies in 
 the cut cell treatment. I would expect that the difference fields in the Sch\"{a}r case are 
 at least qualitatively similar to those exhibited in the theta advection case, which 
 would further confirm the relevance of this advection test as well as the conclusion 
 that errors in the advection of theta through the cut cells may be responsible for the 
 anomalies appearing with this grid.
\end{quotation}
\TODO{the gravity wave amplitude decreases but the advection errors do not.  hence, this is a good choice for the sample line.  we considered plotting heatmaps, but found that it was not as easy to distinguish between the gravity waves and the advection errors.}

>>>>

\begin{quotation}
	Section 4d – Sch\"{a}r mountain-wave tests. These tests are more interesting now that 
 the case has been simulated with a variety of grid resolutions. However, I'm 
 surprised that the analyses of these results seem to focus on behavior far 
 downstream of the mountain, as is evident in Figs. 6 and 7. I'm not aware of any 
 published results that extend beyond x = 25 km in Fig. 6. Since the amplitude of the 
 disturbances are decaying with downstream distance, small inaccuracies in behavior 
 of the absorbing layer and boundary conditions have larger impact such that the 
 relative errors in comparison to the analytic solution become large. (Note, for 
 example the erroneous extension of negative perturbation theta contours to the 
 surface at x = 25 km in Fig. 6.)  All we learn from Fig. 7b is that errors in theta near 
 the surface in the cut-cell cases, which must have been produced in the vicinity of the 
 terrain, continue to be swept downstream. I think it would be more informative to 
 focus on solution differences between the BTF and cut-cell results near the terrain as 
 is done in Fig. 8 for the terrain-following theta advection. The authors could display 
 these difference fields for the various grid resolutions in exactly the same manner as 
 in Fig. 8. The theta advection test presented by the authors is a very nice complement 
 to the gravity-wave tests. It confirms that the BTF solution is behaving properly and 
 therefore lends support to interpreting differences in the two grids as inaccuracies in 
 the cut cell treatment. I would expect that the difference fields in the Sch\"{a}r case are 
 at least qualitatively similar to those exhibited in the theta advection case, which 
 would further confirm the relevance of this advection test as well as the conclusion 
 that errors in the advection of theta through the cut cells may be responsible for the 
 anomalies appearing with this grid.
\end{quotation}
We considered plotting heatmaps but found that it was not easy to distinguish between gravity waves and numerical errors.  The position of the sample line was chosen so that numerical errors would be revealed more clearly: far away from the mountain, the wave amplitude is small but the potential temperature errors remain constant in the lee of the mountain.  The manuscript now explains this choice at line \TODO{xxx}.

### 2016-01-05 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
justify sample line position

At $\Delta z = \SI{300}{\meter}$, vertical velocities on the BTF and cut cell grids are visually indistinguishable (not shown).  They agree with the high resolution mass-conserving semi-implicit semi-Lagrangian solution from \citet{melvin2010}.
The initial thermal profile is subtracted from the potential temperature field at the end of the integration to reveal the structure of thermal anomalies.  The anomalies on the BTF grid with $\Delta z = \SI{50}{\meter}$ is shown in figure~\ref{fig:gw-theta}.  A vertical profile is taken at $x = \SI{50}{\kilo\meter}$, marked by the dashed line in figure~\ref{fig:gw-theta}, with results shown for the BTF grids in figure~\ref{fig:gw-sampleLine}a and on the cut cell grids in figure~\ref{fig:gw-sampleLine}b.
\TODO{say why x=50km is a good place to take these measurements.}
On all grids, potential temperature differences increase with height in the lowest \SI{1200}{\meter} at $x = \SI{50}{\kilo\meter}$, in agreement with the results seen in figure~\ref{fig:gw-theta}.  Results are seen to converge on all grids, with the exception of small errors in the lowest layers on the cut cell grids.

>>>>

At $\Delta z = \SI{300}{\meter}$, vertical velocities on the BTF and cut cell grids are visually indistinguishable (not shown).  They agree with the high resolution mass-conserving semi-implicit semi-Lagrangian solution from \citet{melvin2010}.
The initial thermal profile is subtracted from the potential temperature field at the end of the integration to reveal the structure of thermal anomalies.  The anomalies on the BTF grid with $\Delta z = \SI{50}{\meter}$ is shown in figure~\ref{fig:gw-theta}.  A vertical profile is taken at $x = \SI{50}{\kilo\meter}$, marked by the dashed line in figure~\ref{fig:gw-theta}, with results shown for the BTF grids in figure~\ref{fig:gw-sampleLine}a and on the cut cell grids in figure~\ref{fig:gw-sampleLine}b.
The position is chosen to be far away from the mountain where the gravity wave amplitude is small in order to better reveal numerical errors.
On all grids, potential temperature differences increase with height in the lowest \SI{1200}{\meter} at $x = \SI{50}{\kilo\meter}$, in agreement with the results seen in figure~\ref{fig:gw-theta}.  Results are seen to converge on all grids, with the exception of small errors in the lowest layers on the cut cell grids.
